A survey of HTTP caching options on the open Web

### 2015-01-14 sanity/paper1.tex
Promote lifetime problems to future work
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@984 43ef1190-90fd-4dd7-a769-d0121f02b80e

@@

Data owners should seek to understand their change frequency, and
adjust cache headers accordingly. Framework authors should make it
easy to set the expected lifetime, and manage changes to the
publishing schedule.

>>>>

Estimating the freshness lifetime is a challenging problem for data
owners. It must necessarily involve the human users involved in the
publishing cycle since they are making a committment about future
changes. Designing user support systems as well as interfaces that fit
the publisher's workflow, is an important problem.

@@

In many cases, setting a reasonable cache headers is straightforward,
and should be done by data owners. Framework authors should make it
easy to set the expected lifetime.
